Supplement - Sexually dimorphic repression of germline identity by the X-linked intellectual disability gene KDM5C

### 2024-09-25 submission/supplement.Rmd
edits

---
title: Supplement - Erosion of somatic tissue identity with loss of the X-linked intellectual disability factor KDM5C
output: pdf_document
geometry: margin = 1in
font-size: 11pt
header-includes:
   - \renewcommand{\figurename}{Supplementary Figure}
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \usepackage{siunitx}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}

@@

**Supplementary table 5: Germline gene CpG islands and promoter CpG methylation.** 1) enrichPlot gene ontology results of germline genes with and without CpG islands (CGIs) within their promoter (TSS &#177; 500 bp). 2) methylKit whole genome bisulfite sequencing (WGBS) results table comparing germline gene promoter CpG methylation (TSS &#177; 500 bp) in male wild-type ESCs versus wild-type extended EpiLCs (exEpiLCs). 3) methylKit WGBS results table comparing germline gene promoter CpG methylation in male _Kdm5c_-KO versus wild-type exEpiLCs.

>>>>

---
title: Supplement - Sexually dimorphic repression of germline identity by the X-linked intellectual disability gene KDM5C
output: pdf_document
geometry: margin = 1in
font-size: 11pt
header-includes:
   - \renewcommand{\figurename}{Supplementary Figure}
   - \usepackage{caption}
   - \captionsetup[figure]{font=footnotesize, labelfont=bf}
   - \usepackage{sectsty} 
   - \usepackage{helvet}
   - \renewcommand{\familydefault}{\sfdefault}
   - \usepackage{lineno}
   - \linenumbers
   - \renewcommand\linenumberfont{\normalfont\small}
   - \usepackage{setspace}
   - \usepackage{siunitx}
   - \spacing{1.5}
   - \pagenumbering{arabic}
   - \usepackage{indentfirst}

@@

**Supplementary table 5: Germline gene CpG islands and promoter CpG methylation.** 1) enrichPlot gene ontology results of germline genes with and without CpG islands (CGIs) within their promoter (TSS &#177; 500 bp). 2) methylKit whole genome bisulfite sequencing (WGBS) results table comparing germline gene promoter CpG methylation (TSS &#177; 500 bp) in male wild-type ESCs versus wild-type extended EpiLCs (exEpiLCs). 3) methylKit WGBS results table comparing germline gene promoter CpG methylation in male _Kdm5c_-KO versus wild-type exEpiLCs. 4) enrichPlot gene ontology results of promoters hypomethylated in _Kdm5c_-KO exEpiLCs
